### 2016-06-24 paper/numerical_experiments.tex
garlic

The domain divisions for the three adaptive iterations are shown in Figure~\ref{fig:divvy3D}. We see that the error decomposition causes the first refinement iteration to target the QoI region and observations. Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy1_whitebg_shiftaxes.png} 
\caption{MF$_1$}
\label{fig:ref3D_1}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy2_whitebg_shiftaxes.png} 
\caption{MF$_2$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy3_whitebg_shiftaxes.png} 
\caption{MF$_3$}
\end{subfigure}
\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
\label{fig:divvy3D}
\end{figure} 
The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations. Refining a larger region per iteration runs the risks of refining in the wrong areas due to linearization about a $\Psi_{MF}$ that is very different from $\Psi_{HF}$, but can also allow one to reach the chosen error tolerance in fewer iterations and less runtime. We compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose the $5\%$ of the basis functions with the largest error for model refinement. Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and Figure~\ref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
\begin{table}
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
& & & (Estimated) & (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
MF01 & 9.27 & 613419  & -0.06649 & -0.10759 & 1040 \\
MF02 & 16.9 & 558523  & 0.00208  & -0.01988 & 1860 \\
MF03 & 23.7 & 550323  & 0.00456  & -0.00528 & 2420 \\
MF04 & 30.4 & 548225  & 0.00302  & -0.00147 & 2970 \\
MF05 & 37.2 & 547744  & 0.00120  & -0.00059 & 3309 \\
MF06 & 44.6 & 547532  & 0.00035  & -0.00020 & 3642 \\
HF   & 100  & 547420  & 0        & 0        & 6210 \\
\end{tabular}
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration.}
\label{tab:ref3D_dainty}
\end{table}
\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy1_whitebg_shiftaxes.png} 
\caption{MF$_1$}
\label{fig:ref3d_dainty1}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy2_whitebg_shiftaxes.png} 
\caption{MF$_2$}
\label{fig:ref3d_dainty2}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy3_whitebg_shiftaxes.png} 
\caption{MF$_3$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy4_whitebg_shiftaxes.png} 
\caption{MF$_4$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy5_whitebg_shiftaxes.png} 
\caption{MF$_5$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy6_whitebg_shiftaxes.png} 
\caption{MF$_6$}
\end{subfigure}
\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
\label{fig:divvy3D_dainty}
\end{figure} 
We again observe that the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign. It can also be seen in Figure~\ref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations. Similarly to the examples in Section~\ref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.

>>>>

The domain divisions for the three adaptive iterations are shown in Figure~\ref{fig:divvy3D}. We see that the error decomposition causes the first refinement iteration to target the QoI region and observations. Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
%
\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy1_whitebg_shiftaxes.png} 
\caption{MF$_1$}
\label{fig:ref3D_1}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy2_whitebg_shiftaxes.png} 
\caption{MF$_2$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p1/divvy3_whitebg_shiftaxes.png} 
\caption{MF$_3$}
\end{subfigure}
\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
\label{fig:divvy3D}
\end{figure} 
%

The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations. Refining a larger region per iteration runs the risks of refining in the wrong areas due to linearization about a $\Psi_{MF}$ that is very different from $\Psi_{HF}$, but can also allow one to reach the chosen error tolerance in fewer iterations and less runtime. We compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose the $5\%$ of the basis functions with the largest error for model refinement.

Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and Figure~\ref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
%
\begin{table}
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
& & & (Estimated) & (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
MF01 & 9.27 & 613419  & -0.06649 & -0.10759 & 1040 \\
MF02 & 16.9 & 558523  & 0.00208  & -0.01988 & 1860 \\
MF03 & 23.7 & 550323  & 0.00456  & -0.00528 & 2420 \\
MF04 & 30.4 & 548225  & 0.00302  & -0.00147 & 2970 \\
MF05 & 37.2 & 547744  & 0.00120  & -0.00059 & 3309 \\
MF06 & 44.6 & 547532  & 0.00035  & -0.00020 & 3642 \\
HF   & 100  & 547420  & 0        & 0        & 6210 \\
\end{tabular}
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration.}
\label{tab:ref3D_dainty}
\end{table}
%
\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy1_whitebg_shiftaxes.png} 
\caption{MF$_1$}
\label{fig:ref3d_dainty1}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy2_whitebg_shiftaxes.png} 
\caption{MF$_2$}
\label{fig:ref3d_dainty2}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy3_whitebg_shiftaxes.png} 
\caption{MF$_3$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy4_whitebg_shiftaxes.png} 
\caption{MF$_4$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy5_whitebg_shiftaxes.png} 
\caption{MF$_5$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/run_0p05/divvy6_whitebg_shiftaxes.png} 
\caption{MF$_6$}
\end{subfigure}
\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
\label{fig:divvy3D_dainty}
\end{figure} 
%
We again observe that the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign. It can also be seen in Figure~\ref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations. Similarly to the examples in Section~\ref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.
